Associations between Chlorophyll \emph{a} and various Microcystin-LR Health Advisory Concentrations

### 2015-09-10 manuscript/manuscript.Rmd
reorg tables and figures, rerender pdf

################################################################################
# Condtional Probability
################################################################################
mc_guides <- c(0.3, 1, 1.6, 2, 4, 10, 20)
mc_names <- c("EPA_Child","WHO","EPA_Adult","WHO","WHO","WHO","WHO")
mc_chla <- vector("numeric",length(mc_guides))

epa_child_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log10(mc_guides[1]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100)

@@

who_drink_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log10(mc_guides[2]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100)

@@

epa_adult_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log10(mc_guides[3]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100)

@@

who_rec_low1_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log10(mc_guides[4]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100)

@@

who_rec_low2_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log10(mc_guides[5]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100)

@@

who_rec_med1_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log10(mc_guides[6]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100)

@@

who_rec_med2_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log10(mc_guides[7]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100)

@@

Chlorophyll *a* is a very commonly measured components of water quality that is also known to be associated with Microsystin-LR concentrations [REFS].  Additionally there are many rapid measurements for assessing chlorophyll *a* levels *in situ*.  For instance, there are small or hand held flourometers that provide reliable measurements [REFS].   Given these facts, it might be possible to identify chlorophyll *a* concentrations that would be associated with the various Microcystin-LR health advisory levels.  Identifying these associations would provide another reliable tool for water resource managers to use to help manage the threat to public health posed by cHABs and would be especially useful in the absence of microcystin-LR concentrations.  Thus, the goal of this paper is to utlize the National Lakes Assessment data and identify chlorophyll *a* concentrations that are associated with higher probabilities of exceeding several microcystin-LR health advisory concentrations [NLA REF].  So that others may repeat this analysis, the data, code, and this manuscript are freely available via [https://github.com/USAPE/microcystinchla](https://github.com/USAPE/microcystinchla).

#Methods

```{r microcystin_levels,echo=FALSE,results='asis'}
source_of_stnd <- c("WHO",
                    "WHO",
                    "WHO",
                    "WHO",
                    "WHO",
                    "U.S. EPA",
                    "U.S. EPA")
type_of_stnd <- c("Recreational",
                  "Recreational",
                  "Recreational",
                  "Recreational",
                  "Drinking",
                  "Drinking",
                  "Drinking")
concentration <- c("2-4 ug/l",
                   "10-20 ug/l",
                   "20-2000 ug/l",
                   ">2000 ug/l",
                   "1 ug/l",
                   "0.3 ug/l",
                   "1.6 ug/l")
#note <- c("Low probability of adverse health effects",
#          "Moderate probability of adverse health effects",
#          "High probability of adverse health effects, These higher #concentrations typically only seen in visible scums/algal mats",
#          "Very high probability of adverse health effects",
#          "",
#          "Children younger than school age",
#          "Individuals School age and older")
mc_conc_table <- data.frame(source_of_stnd, type_of_stnd, concentration) %>%
  arrange(type_of_stnd)
names(mc_conc_table)<-c("Source","Type","Concentration")
pandoc.table(mc_conc_table,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
```

We evaluated associated chlorophyll *a* concentrations for an effect for each of the WHO and EPA levels. Lakes with higher microcystin-LR concentrations were rare. Only `r 100*(length(nla_dat$MCYST_TL_UGL[nla_dat$MCYST_TL_UGL>=10])/nrow(nla_dat))` % of lakes sampled had a concentration greater than 10.  For this analysis we focus on the microcystin concentrations that are better represented in the NLA data. These were  0.3, 1, 1.6, and 2 $\mu$g/L.

@@

```{r mc_chla_table, results='asis', echo=FALSE}
mc_chla_tbl <- data.frame(Source=mc_names,Microcystin=mc_guides,Chlorophyll=mc_chla)[1:4,]
pandoc.table(mc_chla_tbl,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
```

@@

```{r epa_child_cp_plot,echo=FALSE}
plot_cp(epa_child_cp,x = "Log 10 Chlorophyll", y = "Probability of Exceeding EPA Child HA")
```

@@

```{r who_drink_cp_plot,echo=FALSE}
plot_cp(who_drink_cp, x = "Log 10 Chlorophyll", y = "Probability of Exceeding WHO Drinking HA")
```

@@

```{r epa_adult_cp ,echo=FALSE}
plot_cp(epa_adult_cp, x = "Log 10 Chlorophyll", y = "Probability of Exceeding EPA Adult HA")
```

@@

```{r who_rec_low1_cp, echo=FALSE}
plot_cp(who_rec_low1_cp, x = "Log 10 Chlorophyll", y = "Probability of Exceeding WHO Low Probability HA")
```

@@

>>>>

################################################################################
# Condtional Probability
################################################################################
mc_guides <- c(0.3, 1, 1.6, 2, 4, 10, 20)
mc_names <- c("U.S. EPA","WHO","U.S. EPA","WHO","WHO","WHO","WHO")
mc_type <- c("Drinking","Drinking","Drinking","Recreational","Recreational","Recreational","Recreational")
mc_chla <- vector("numeric",length(mc_guides))
wgt <- nla_dat$WGT_NLA
#wgt<- rep(1,nrow(nla_dat))

epa_child_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log10(mc_guides[1]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100, xW=wgt)

@@

who_drink_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log10(mc_guides[2]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100, xW=wgt)

@@

epa_adult_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log10(mc_guides[3]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100, xW=wgt)

@@

who_rec_low1_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log10(mc_guides[4]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100, xW=wgt)

@@

who_rec_low2_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log10(mc_guides[5]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100, xW=wgt)

@@

who_rec_med1_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log10(mc_guides[6]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100, xW=wgt)

@@

who_rec_med2_cp <- condprob(xX = nla_dat$log_chla,xY = nla_dat$log_micro, 
                     xImpair = log10(mc_guides[7]), ProbComp = "gt", Exceed = "gte",
                     ci = TRUE, R = 100, xW=wgt)

@@

Chlorophyll *a* is a very commonly measured components of water quality that is also known to be associated with Microsystin-LR concentrations [REFS].  Additionally there are many rapid measurements for assessing chlorophyll *a* levels *in situ*.  For instance, there are small or hand held flourometers that provide reliable measurements [REFS].   Given these facts, it might be possible to identify chlorophyll *a* concentrations that would be associated with the various Microcystin-LR health advisory levels.  Identifying these associations would provide another reliable tool for water resource managers to use to help manage the threat to public health posed by cHABs and would be especially useful in the absence of microcystin-LR concentrations.  Thus, the goal of this paper is to utlize the National Lakes Assessment data and identify chlorophyll *a* concentrations that are associated with higher probabilities of exceeding several microcystin-LR health advisory concentrations [NLA REF].  So that others may repeat or adjust this analysis, the data, code, and this manuscript are freely available via [https://github.com/USAPE/microcystinchla](https://github.com/USAPE/microcystinchla).

#Methods
We evaluated associated chlorophyll *a* concentrations for an effect for each of the WHO and U.S. EPA levels (Table \ref{tab:microcystin_levels}). Lakes with higher microcystin-LR concentrations were rare. Only `r round(100*(length(nla_dat$MCYST_TL_UGL[nla_dat$MCYST_TL_UGL>=10])/nrow(nla_dat)),2)` % of lakes sampled had a concentration greater than 10.  For this analysis we focus on the microcystin concentrations that are better represented in the NLA data. These were  0.3, 1, 1.6, and 2 $\mu$g/L.

@@

(Table \ref{tab:mc_chla_table})

(Figure \ref{fig:epa_child_cp_plot})

(Figure \ref{fig:who_drink_cp_plot})

(Figure \ref{fig:epa_adult_cp})

(Figure \ref{fig:who_rec_low1_cp})

@@

```{r epa_child_cp_plot,echo=FALSE, fig.cap="Plot of \\label{fig:epa_child_cp_plot}"}
plot_cp(epa_child_cp,x = "Log 10 Chlorophyll", y = "Probability of Exceeding EPA Child HA")
```

@@

```{r who_drink_cp_plot,echo=FALSE, fig.cap="Plot of  \\label{fig:who_drink_cp_plot}"}
plot_cp(who_drink_cp, x = "Log 10 Chlorophyll", y = "Probability of Exceeding WHO Drinking HA")
```

@@

```{r epa_adult_cp ,echo=FALSE, fig.cap="Plot of  \\label{fig:epa_adult_cp}"}
plot_cp(epa_adult_cp, x = "Log 10 Chlorophyll", y = "Probability of Exceeding EPA Adult HA")
```

@@

```{r who_rec_low1_cp, echo=FALSE, fig.cap="Plot of  \\label{fig:who_rec_low1_cp}"}
plot_cp(who_rec_low1_cp, x = "Log 10 Chlorophyll", y = "Probability of Exceeding WHO Low Probability HA")
```

@@

#Tables

```{r microcystin_levels,echo=FALSE,results='asis', fig.cap="Various suggested microcystin-LR health advisory concentrations. \\label{fig:microcystin_levels}"}
source_of_stnd <- c("WHO",
                    "WHO",
                    "WHO",
                    "WHO",
                    "WHO",
                    "U.S. EPA",
                    "U.S. EPA")
type_of_stnd <- c("Recreational",
                  "Recreational",
                  "Recreational",
                  "Recreational",
                  "Drinking",
                  "Drinking",
                  "Drinking")
concentration <- c("2-4 ug/l",
                   "10-20 ug/l",
                   "20-2000 ug/l",
                   ">2000 ug/l",
                   "1 ug/l",
                   "0.3 ug/l",
                   "1.6 ug/l")
#note <- c("Low probability of adverse health effects",
#          "Moderate probability of adverse health effects",
#          "High probability of adverse health effects, These higher #concentrations typically only seen in visible scums/algal mats",
#          "Very high probability of adverse health effects",
#          "",
#          "Children younger than school age",
#          "Individuals School age and older")
mc_conc_table <- data.frame(source_of_stnd, type_of_stnd, concentration) %>%
  arrange(type_of_stnd)
names(mc_conc_table)<-c("Source","Type","Concentration")
pandoc.table(mc_conc_table,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
```

```{r mc_chla_table, results='asis', echo=FALSE, fig.cap="Chlorophyll \textit{a} concentrations that are associated with a 50% probability of exceeding a microcystin-LR health advisory concentration. \\label{fig:mc_chla_table}"}
mc_chla_tbl <- data.frame(Source=mc_names,Type=mc_type,Microcystin=mc_guides,Chlorophyll=mc_chla)[1:4,]
pandoc.table(mc_chla_tbl,justify = "left" ,split.table = 120, split.cells  = c(20,20,20))
```

### 2015-09-10 manuscript/manuscript.tex
reorg tables and figures, rerender pdf

Cyanobacteria harmful algal blooms (cHABs) are associated with a wide
range of adverse health effects that stem mostly from the presence of
cyanotoxins. To help protect against these impacts, several health
advisory levels have been set for some toxins. In particular, one of the
more common toxins, microcystin, has several advisory levels set for
drinking water and recreational use and managing water bodies to meet
those levels could have far reaching benefits. However, compared to
other water quality measures, measurements of microcystin are not common
and current field measurement techniques have limited precision and
accuracy. Addressing these issues will take time and resources. Thus,
there is utility in finding indicators of microcystin that are already
widely available, can be estimated quickly and \emph{in situ}, and used
as a first defense against high levels of microcystin. In particular,
chlorophyll \emph{a} is very commonly measured, can be estimated
\emph{in situ}, and has been shown to be positively associated with
microcystin. In this paper we use this association to provide estimates
of chlorophyll \emph{a} that if exceeded would be indicative of a higher
probability of exceeding select health advisory concentrations for
microcystin-LR. Using the 2007 National Lakes Assessment and a
conditional probability approach that has been used in other water
quality settings, we identify chlorophyll \emph{a} concentrations that
are more likely than not to be associated with an exceedance of a
microcystin health advisory level. We look at the recent US EPA
standards for drinking water as well as the World Health Organization
levels for drinking water and recreational use. For microcystin
concentrations of 0.3, 1, 1.6, and 2 we find chlorophyll \emph{a}
concentrations of 25.1, 69.6, 84.96, and 113.14, respectively. When
managing for these various microcystin levels exceeding these reported
chlorophyll \emph{a} concentrations should be a trigger for further
testing and possible management action.

@@

Chlorophyll \emph{a} is a very commonly measured components of water
quality that is also known to be associated with Microsystin-LR
concentrations {[}REFS{]}. Additionally there are many rapid
measurements for assessing chlorophyll \emph{a} levels \emph{in situ}.
For instance, there are small or hand held flourometers that provide
reliable measurements {[}REFS{]}. Given these facts, it might be
possible to identify chlorophyll \emph{a} concentrations that would be
associated with the various Microcystin-LR health advisory levels.
Identifying these associations would provide another reliable tool for
water resource managers to use to help manage the threat to public
health posed by cHABs and would be especially useful in the absence of
microcystin-LR concentrations. Thus, the goal of this paper is to utlize
the National Lakes Assessment data and identify chlorophyll \emph{a}
concentrations that are associated with higher probabilities of
exceeding several microcystin-LR health advisory concentrations {[}NLA
REF{]}. So that others may repeat this analysis, the data, code, and
this manuscript are freely available via
\href{https://github.com/USAPE/microcystinchla}{\url{https://github.com/USAPE/microcystinchla}}.

@@

We evaluated associated chlorophyll \emph{a} concentrations for an
effect for each of the WHO and EPA levels. Lakes with higher
microcystin-LR concentrations were rare. Only 1.1616651 \% of lakes
sampled had a concentration greater than 10. For this analysis we focus
on the microcystin concentrations that are better represented in the NLA
data. These were 0.3, 1, 1.6, and 2 \(\mu\)g/L.

@@

\begin{longtable}[c]{@{}lll@{}}
\toprule
\begin{minipage}[b]{0.13\columnwidth}\raggedright\strut
Source
\strut\end{minipage} &
\begin{minipage}[b]{0.18\columnwidth}\raggedright\strut
Microcystin
\strut\end{minipage} &
\begin{minipage}[b]{0.18\columnwidth}\raggedright\strut
Chlorophyll
\strut\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.13\columnwidth}\raggedright\strut
EPA\_Child
\strut\end{minipage} &
\begin{minipage}[t]{0.18\columnwidth}\raggedright\strut
0.3
\strut\end{minipage} &
\begin{minipage}[t]{0.18\columnwidth}\raggedright\strut
25.1
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.13\columnwidth}\raggedright\strut
WHO
\strut\end{minipage} &
\begin{minipage}[t]{0.18\columnwidth}\raggedright\strut
1
\strut\end{minipage} &
\begin{minipage}[t]{0.18\columnwidth}\raggedright\strut
69.6
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.13\columnwidth}\raggedright\strut
EPA\_Adult
\strut\end{minipage} &
\begin{minipage}[t]{0.18\columnwidth}\raggedright\strut
1.6
\strut\end{minipage} &
\begin{minipage}[t]{0.18\columnwidth}\raggedright\strut
84.96
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.13\columnwidth}\raggedright\strut
WHO
\strut\end{minipage} &
\begin{minipage}[t]{0.18\columnwidth}\raggedright\strut
2
\strut\end{minipage} &
\begin{minipage}[t]{0.18\columnwidth}\raggedright\strut
113.1
\strut\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{figure}[htbp]
\centering
\includegraphics{manuscript_files/figure-latex/epa_child_cp_plot-1.pdf}
\caption{}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{manuscript_files/figure-latex/who_drink_cp_plot-1.pdf}
\caption{}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{manuscript_files/figure-latex/epa_adult_cp -1.pdf}
\caption{}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{manuscript_files/figure-latex/who_rec_low1_cp-1.pdf}
\caption{}
\end{figure}

@@

>>>>

Cyanobacteria harmful algal blooms (cHABs) are associated with a wide
range of adverse health effects that stem mostly from the presence of
cyanotoxins. To help protect against these impacts, several health
advisory levels have been set for some toxins. In particular, one of the
more common toxins, microcystin, has several advisory levels set for
drinking water and recreational use and managing water bodies to meet
those levels could have far reaching benefits. However, compared to
other water quality measures, measurements of microcystin are not common
and current field measurement techniques have limited precision and
accuracy. Addressing these issues will take time and resources. Thus,
there is utility in finding indicators of microcystin that are already
widely available, can be estimated quickly and \emph{in situ}, and used
as a first defense against high levels of microcystin. In particular,
chlorophyll \emph{a} is very commonly measured, can be estimated
\emph{in situ}, and has been shown to be positively associated with
microcystin. In this paper we use this association to provide estimates
of chlorophyll \emph{a} that if exceeded would be indicative of a higher
probability of exceeding select health advisory concentrations for
microcystin-LR. Using the 2007 National Lakes Assessment and a
conditional probability approach that has been used in other water
quality settings, we identify chlorophyll \emph{a} concentrations that
are more likely than not to be associated with an exceedance of a
microcystin health advisory level. We look at the recent US EPA
standards for drinking water as well as the World Health Organization
levels for drinking water and recreational use. For microcystin
concentrations of 0.3, 1, 1.6, and 2 we find chlorophyll \emph{a}
concentrations of 20.8, 71.2, 92.16, and 110.16, respectively. When
managing for these various microcystin levels exceeding these reported
chlorophyll \emph{a} concentrations should be a trigger for further
testing and possible management action.

@@

Chlorophyll \emph{a} is a very commonly measured components of water
quality that is also known to be associated with Microsystin-LR
concentrations {[}REFS{]}. Additionally there are many rapid
measurements for assessing chlorophyll \emph{a} levels \emph{in situ}.
For instance, there are small or hand held flourometers that provide
reliable measurements {[}REFS{]}. Given these facts, it might be
possible to identify chlorophyll \emph{a} concentrations that would be
associated with the various Microcystin-LR health advisory levels.
Identifying these associations would provide another reliable tool for
water resource managers to use to help manage the threat to public
health posed by cHABs and would be especially useful in the absence of
microcystin-LR concentrations. Thus, the goal of this paper is to utlize
the National Lakes Assessment data and identify chlorophyll \emph{a}
concentrations that are associated with higher probabilities of
exceeding several microcystin-LR health advisory concentrations {[}NLA
REF{]}. So that others may repeat or adjust this analysis, the data,
code, and this manuscript are freely available via
\href{https://github.com/USAPE/microcystinchla}{\url{https://github.com/USAPE/microcystinchla}}.

@@

We evaluated associated chlorophyll \emph{a} concentrations for an
effect for each of the WHO and U.S. EPA levels (Table
\ref{tab:microcystin_levels}). Lakes with higher microcystin-LR
concentrations were rare. Only 1.16 \% of lakes sampled had a
concentration greater than 10. For this analysis we focus on the
microcystin concentrations that are better represented in the NLA data.
These were 0.3, 1, 1.6, and 2 \(\mu\)g/L.

@@

(Table \ref{tab:mc_chla_table})

(Figure \ref{fig:epa_child_cp_plot})

(Figure \ref{fig:who_drink_cp_plot})

(Figure \ref{fig:epa_adult_cp})

(Figure \ref{fig:who_rec_low1_cp})

@@

\begin{figure}[htbp]
\centering
\includegraphics{manuscript_files/figure-latex/epa_child_cp_plot-1.pdf}
\caption{Plot of \label{fig:epa_child_cp_plot}}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{manuscript_files/figure-latex/who_drink_cp_plot-1.pdf}
\caption{Plot of \label{fig:who_drink_cp_plot}}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{manuscript_files/figure-latex/epa_adult_cp -1.pdf}
\caption{Plot of \label{fig:epa_adult_cp}}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{manuscript_files/figure-latex/who_rec_low1_cp-1.pdf}
\caption{Plot of \label{fig:who_rec_low1_cp}}
\end{figure}

@@

\section{Tables}\label{tables}

\begin{verbatim}
## Warning in split.large.cells(t): length of split.cells vector is smaller
## than data. Default value will be used for other cells
\end{verbatim}

\begin{verbatim}
## Warning in split.large.cells(t.colnames): length of split.cells vector is
## smaller than data. Default value will be used for other cells
\end{verbatim}

\begin{longtable}[c]{@{}llll@{}}
\toprule
\begin{minipage}[b]{0.11\columnwidth}\raggedright\strut
Source
\strut\end{minipage} &
\begin{minipage}[b]{0.16\columnwidth}\raggedright\strut
Type
\strut\end{minipage} &
\begin{minipage}[b]{0.17\columnwidth}\raggedright\strut
Microcystin
\strut\end{minipage} &
\begin{minipage}[b]{0.17\columnwidth}\raggedright\strut
Chlorophyll
\strut\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
U.S. EPA
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Drinking
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
0.3
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
20.8
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
WHO
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Drinking
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
1
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
71.2
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
U.S. EPA
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Drinking
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
1.6
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
92.16
\strut\end{minipage}\tabularnewline
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
WHO
\strut\end{minipage} &
\begin{minipage}[t]{0.16\columnwidth}\raggedright\strut
Recreational
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
2
\strut\end{minipage} &
\begin{minipage}[t]{0.17\columnwidth}\raggedright\strut
110.2
\strut\end{minipage}\tabularnewline
\bottomrule
\end{longtable}
